\subsection{Thread-based Concurrency for UML State Machine}
\label{sec:thread}
This Subsection describes our design for generated code. 
The design is based on an example-based analysis, which is not presented here due to space limitation.

%\input{sections/analysis}




\subsubsection{Thread-based design of generated code}
The concurrency of concurrent UML State Machines is based on multi-thread, in which there are permanent and spontaneous threads. 
While permanent threads (PTs) are created once and live as long as the state machine is alive, spontaneous threads (STs) are spawned in active for a while. 
%The method associated with a permanent thread is a non-deterministic action, which is run in parallel with the main thread. The latter reads and dispatch events from the event queue. 
Each PT is initialized at the state machine initialization. 
%The number of threads associated with NDAs is therefore equal to that of the NDAs.
The design of threads is based on the thread pool pattern, which initializes all threads at once, and the paradigm "wait-execute-wait". 
In the latter, a thread \tb{waits} for a signal to \tb{execute} its associated method and goes back to the \tb{wait} point if it receives a stop signal or its associated method completes. 
Each PT is associated with one of the following actions:
\begin{itemize}
	\item \ti{doActivity} of each state if has. %The number of \ti{doActivity} $n_{do} = \#\{s \in V|\exists doActivity(s)\}$
	
	\item Sleep function associated with a \ti{TimeEvent} which counts ticks and emits a \ti{TimeEvent} once completes.%: $n_{te} = \#\{e \in E|\ti{e is a time event}\}$.
	
	\item Change detect function associated with a \ti{ChangeEvent} which observes a variable or a boolean expression and pushes an event to the queue if changes happen.%: $n_{che} = \#\{e \in E|\ti{e is a change event}\}$.
	
	\item State machine main thread,which reads events from the event queue, and sends start and stop signals to these initial threads.
\end{itemize} 

%Therefore, The number of initial threads is $n_{threads} = n_{do} + n_{te} + n_{che}$ plus a main thread, which reads events from the event queue, and sends start and stop signals to these initial threads. 

Now we consider STs which are spawned by a parent thread, joined until and destroyed once the associated methods complete. 

\begin{comment}
The followings describe different types of DAs:

\begin{itemize}
	\item Actions executed when entering/exiting an orthogonal region, which can be: execute a chain of transition effects contained by the region before entering a stable sub-state or exiting the region completely.%: $n_{region threads} = \#\{r \in \mathcal{R}|ctner(r).kind=conc\}$
	
	\item Effects of transitions outgoing from a $fork$ and those incomings to a $join$.%: \\
	%$\mathcal{J} = \{v \in V|v.kind=join\}$ \\
	%$\mathcal{F} = \{v \in V|v.kind=fork\}$ \\
	%$$n_{FJ\_threads} = \sum_{v \in \mathcal{F}} {\#T_{outs}(v)} + \sum_{v \in \mathcal{J}} {\#T_{ins}(v)}$$.
\end{itemize}
\end{comment}

The STs follow a paradigm in which if a thread $parent$ spawns a set of threads $children$, $parent$ must wait until $children$ complete their associate methods. These threads are spawned in one of the following cases:

\begin{itemize}
	\item A thread is created for each effect of transitions' outgoing from a \ti{fork} or incoming to a \ti{join}.
	
	\item Entering a concurrent state $s$, after the execution of $entry(s)$, a thread is also created for each orthogonal region. 
	
	\item Exiting a concurrent state $s$, before the execution of $exit(s)$, a thread is also created for each region to exit the corresponding active sub-state.
	
	%\item An event is processed by active states, in which a thread per orthogonal region. 
\end{itemize}

\subsubsection{Deadlock avoidance}
Each PT is associated with a mutex for synchronization communication in the multi-thread-based generated code. 
The mutex must be locked before the method associated with the thread is executed. 
The mutex associated with the main thread preserves the run-to-completion semantics since some event such as \ti{CallEvent} can be processed synchronously and some asynchronously. Each event processing must lock the main mutex before executing the actual processing. 
%Deadlock is one of the main issues in designing multi-thread applications, in which two competing actions wait for the other to finish. In our case, 


\begin{comment}
\begin{tabular}{p{4.0cm}|p{4.0cm}}
Example code generated for doActivity  &  Option  2\\
\begin{lstlisting}[language=C++]
void doActivity(int stateId) {
  isStarts[stateId] = false;
  while(true) {
    mutex[stateId].lock();
    while(!isStarts[stateId]) {
      mutex[stateId].wait();
    }
    states[stateId].doActivity();
    isStarts[stateId] = false;
    mutex[stateId].unlock();
    if (!isStops[stateId]) {
      if (stateId == IDLE_ID || stateId == DISPENSEMONEY_ID ...) {
	    pushCompletionEvent(stateId);
	  }
    }
  }
}
	\end{lstlisting}&
	\begin{lstlisting}
	#include <stdio.h>
	
	int main()
	{
	printf("Hello world\n");
	}
	\end{lstlisting}
\end{tabular} 
\end{comment}
